### 2015-06-15 writing/S'15 LSTM/intro.tex
Comment replies.

%\paragraph{Related work}
%Recent successes on parsing by 
Our results engage with those of \newcite{vinyals2014grammar} and \newcite{dyer2015transition}, who find that sequence models can learn to recognize syntactic structure in natural language, at least when trained on explicitly syntactic tasks. The simplest model presented in Vinyals et al.~uses an LSTM sequence model to encode each sentence as a vector, and then generates a linearized parse (a sequence of brackets and constituent labels) with high accuracy using only the information present in the vector. This shows that the LSTM was able to identify the correct syntactic structures and also hints that it was able to develop a generalizable method for encoding these structures in vectors. However, the massive size of the dataset needed to train the model---250M tokens---leaves open the possibility that it primarily learned to generate only tree structures that it had already seen, representing them as simple hashes rather than structured objects.
% CDM: I wonder about just leaving this next sentence out
If the model were able to map unseen sentences to familiar structures using these hashed representations, it could plausibly have achieved the strong results shown in that paper without actually representing recursive structure, at least in a way that would generalize to substantially new structures.
However, our experiments show that LSTMs can manipulate tree-structured data, suggesting that there are no fundamental obstacles to this kind of generalization.

>>>>

%\paragraph{Related work}
%Recent successes on parsing by 
Our results engage with those of \newcite{vinyals2014grammar} and \newcite{dyer2015transition}, who find that sequence models can learn to recognize syntactic structure in natural language, at least when trained on explicitly syntactic tasks. The simplest model presented in Vinyals et al.~uses an LSTM sequence model to encode each sentence as a vector, and then generates a linearized parse (a sequence of brackets and constituent labels) with high accuracy using only the information present in the vector. This shows that the LSTM was able to identify the correct syntactic structures and also hints that it was able to develop a generalizable method for encoding these structures in vectors. However, the massive size of the dataset needed to train the model---250M tokens---leaves open the possibility that it primarily learned to generate only tree structures that it had already seen, representing them as simple hashes---which would not capture unseen tree structures---rather than as structured objects.
% CDM: I wonder about just leaving this next sentence out
% If the model were able to map unseen sentences to familiar structures using these hashed representations, it could plausibly have achieved the strong results shown in that paper without actually representing recursive structure, at least in a way that would generalize to substantially new structures.
Our experiments, though, show that LSTMs can manipulate tree-structured data, suggesting that there is no fundamental obstacle to this kind of generalization.

### 2015-06-15 writing/S'15 LSTM/methods.tex
Comment replies.

\begin{figure*}[t]
  \centering
  \begin{subfigure}[t]{0.04\textwidth}
      \includegraphics[height=1.45in]{scale.pdf}
\end{subfigure}
\begin{subfigure}[t]{0.24\textwidth}
  \includegraphics[height=1.45in]{fig3c.pdf}
  \caption{Training on sz. $\le$3.}
  \end{subfigure}~~~
\begin{subfigure}[t]{0.24\textwidth}
    \includegraphics[height=1.45in]{fig4c.pdf}
  \caption{Training on sz. $\le$4.}
  \end{subfigure}~~~~
\begin{subfigure}[t]{0.24\textwidth}
      \includegraphics[height=1.45in]{fig6c.pdf}
  \caption{Training on sz. $\le$6.}
\end{subfigure}~~
\begin{subfigure}[t]{0.08\textwidth}
      \includegraphics[height=1.45in]{leg.pdf}
\end{subfigure}
  \caption{Results on three experiments with increasingly rich training sets. The horizontal axis on each graph divides the test set data points (expression pairs) into bins by the number of logical operators in the more complex of the two expressions in the pair. The dotted line shows the size we trained on up to.}
  \label{prop-results} 
\end{figure*}

>>>>

\begin{figure*}[t]
  \centering
  \begin{subfigure}[t]{0.04\textwidth}
      \includegraphics[height=1.45in]{scale.pdf}
\end{subfigure}
\begin{subfigure}[t]{0.24\textwidth}
  \includegraphics[height=1.45in]{fig3c.pdf}
  \caption{Training on sz. $\le$3.}
  \end{subfigure}~~~
\begin{subfigure}[t]{0.24\textwidth}
    \includegraphics[height=1.45in]{fig4c.pdf}
  \caption{Training on sz. $\le$4.}
  \end{subfigure}~~~~
\begin{subfigure}[t]{0.24\textwidth}
      \includegraphics[height=1.45in]{fig6c.pdf}
  \caption{Training on sz. $\le$6.}
\end{subfigure}~~
\begin{subfigure}[t]{0.08\textwidth}
      \includegraphics[height=1.45in]{leg.pdf}
\end{subfigure}
  \caption{Test accuracy on three experiments with increasingly rich training sets. The horizontal axis on each graph divides the test set expression pairs into bins by the number of logical operators in the more complex of the two expressions in the pair. The dotted line shows the size we trained on up to.}
  \label{prop-results} 
\end{figure*}
